%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

\title{Resume_2}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Prathmesh}{Desai}{ % Your name
  \urlstyle{same}\url{http://www.prathmeshdesai.com} \\ % Your website, LinkedIn profile or other web address
  \href{mailto:prathmesh.desai@uwaterloo.ca}{prathmesh.desai@uwaterloo.ca} | 519.722.8110 \\ % Your contact information
  Permanent Address: 2650 Meadow Ridge Dr, Prosper, TX, USA, 75078 \\
  Temporary Address: Unit B - 249 Albert St, Waterloo, ON, Canada, N2L 3T7 \\
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Status
%------------------------------------------------

\section{Legal Status} 

Citizen of Canada \\
Permanent Resident of The United States \\
Overseas Citizen of India

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{University of Waterloo}

\descript{Candidate for Bachelor of Computer Science}
\location{Expected May 2019 | Waterloo, ON}

\sectionspace % Some whitespace after the section

%------------------------------------------------

% \subsection{Wilfred Laurier University}

% \descript{Candidate for Bachelor of Business Administration}
% \location{Expected Aug 2019 | Waterloo, ON}

% \sectionspace % Some whitespace after the section

%------------------------------------------------

% \subsection{Farragut High School}
% 
% \descript{HS Diploma}
% \location{Grad. May 2014 | Knoxville, TN}
% 
% \sectionspace % Some whitespace after the section


%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

Functional Programming \\
Algo. Design \& Data Abstraction \\
Logic \& Computation \\
Data Structures \\
Sequential Programs \\
Adv. Intro to Combinatorics \\
AP Computer Science (HS)

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\vspace{2mm}

\subsection{Programming}

\begin{tabular}{ c c c }
HTML    & CSS    & jQuery \\
JS      & Python & Swift    \\
Clojure & SQL    & LISP   \\
C       & C++    & Java \\
\end{tabular}

\vspace{4mm}

\subsection{Web Servers/Services}

\begin{tabular}{ c c c }
  Apache & Nginx & RESTful \\
  SOAP & IIS & OAuth 2.0
\end{tabular}

\vspace{4mm}

\subsection{Frameworks}

\begin{tabular}{ c c c }
  Express & Jade & Rails \\
  React & React Native & Django \\
  Meteor & Angular & Laravel
\end{tabular}

\vspace{4mm}

\subsection{Backend Technologies}

\begin{tabular}{ c c c }
  MongoDB & Redis & MySQL \\
  AWS S3 & PostgreSQL & GraphQL
\end{tabular}

\vspace{4mm}

\subsection{Graphics}

\begin{tabular}{ c c c }
  Photoshop & Illustrator & InDesign \\
  Maya & Blender & Sketch
\end{tabular}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------


\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% About Me
%------------------------------------------------

My passion for Computer Science stems from both a desire to invent,
and an immense amount of intellectual curiosity for machines. This
pintrigue started when my sixth grade self found
out about the destructive power of {\it rm -rf /} and bash scripts.
Ever since then I have continued to further my programming
expertise by hacking on side-projects, freelance work,
reading books, and working at rising startups.
  
%------------------------------------------------

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Course-Taught Technologies}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightitemize}

    \item \textbf{Visual Studio \& Visual Basic} - Taught in Programming I
    \item \textbf{Java} - Read \textit{Java: The Complete Reference, Ninth Edition} \& AP Computer Science \& Java/J2EE Training through H2KInfosys
    \item \textbf{Python} - Read \textit{Learning Python by Mark Lutz} \& Learned/Used in University of Tennessee Research Internship
    \item \textbf{HTML/CSS/JS} - Learned by revamping the www.hubdoc.com website and Udemy
    \item \textbf{NodeJS and ReactJS} - Work Experience at FarmLogs and Udemy Courses
    \item \textbf{Swift for iOS} Udemy's \textit{The Complete iOS8 and Swift Course: Learn by Building 15 Real World Applications} taught by Mr Rob Percival
    \item \textbf{Maya} - Maya 2015 Tutorial Course offered by Digital-Tutors
    \item \textbf{MATLAB} - Taught by The Vanderbilt University Summer PAVE Program
    
\end{tightitemize}

\subsection{Self-taught Technologies}

{\sl \textbf{Programming Languages (excl. languages mentioned above):}} C, C++, \LaTeX, LISP, C\#, F\# \\
{\sl \textbf{Web Technologies:}} MySQL, Ruby on Rails, Clojure, CoffeeScript, Backbone, React \\
{\sl \textbf{Software:}} Microsoft Office, Photoshop, Dreamweaver, Lightroom, Solidworks, 3DS Max, Blender, Maya, Eclipse, After Effects, Premiere Pro, XCode \\

\subsection{MISCELLANEOUS}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightitemize}

	\item \textbf{Theater Nerd} - Ever since I attended my first improv comedy sketch show, I fell in love with Theater. This passion of mine has led me to be a more outgoing, fun to be around, and funny person.
    \item \textbf{Writer} - Writing is my favorite pastime. I have begun writing a book, and often spend my off hours writing short stories.
    
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}


%------------------------------------------------

\runsubsection{Self Employed}
\descript{| Freelancer}

\location{Spring 2006 – Present | Toronto, ON \& Knoxville, TN \& Waterloo, ON}
\begin{tightitemize}
\item Through numerous freelancing websites and online job postings I took part in a wide array of projects.
\item Project Categories include: Essay-writing, Web Design \& Development, App Design \& Development, 3D Animation, and Video \& Photo Editing
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
\runsubsection{Horizons School of Technology}
\descript{| Jr. Software Engineering Intern / Instructor }

\location{January 2017 – May 2017 | San Francisco, CA}
\begin{tightitemize}
\item Instruct students on CS topics (incl. HTML/CSS, React, Angular, Node, MongoDB, Git, Github, Express, Handlebars...)
\item Develop Curriculum
\item Engineering Lead for local contract projects
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

% \runsubsection{CompuString}
% \descript{| CEO \& Founder}

% \location{Summer 2013 – Present | Knoxville, TN \& Waterloo, ON}
% \begin{tightitemize}
% \item After Excelgrade e-Learning became a success, decided to similarly provide jobs to unemployed computer scientists and software engineers through a software/programming language tutoring service.
% \item Designed and Developed the website for consumers to get information on the variety of courses offered.
% \item Due to high course load in HS and University, did not teach too many customers
% \end{tightitemize}

% \sectionspace % Some whitespace after the section

% %------------------------------------------------

% \runsubsection{Self Employed}
% \descript{| Freelancer}

% \location{Spring 2006 – Present | Toronto, ON \& Knoxville, TN \& Waterloo, ON}
% \begin{tightitemize}
% \item Through numerous freelancing websites and online job postings I took part in a wide array of projects.
% \item Project Categories include: Essay-writing, Web Design \& Development, App Design \& Development, 3D Animation, and Video \& Photo Editing
% \end{tightitemize}

% \sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

\runsubsection{FarmLogs}
\descript{| Front End SE Intern }

\location{January 2016 – May 2016 | Ann Arbor, MI}
\begin{tightitemize}
\item Managed the FarmLogs Web Application and Static Marketing Site
\item Worked using Agile and Waterfall Software Development Methods
\item Code re-factoring from Backbone Views to React Classes
\item Wrote Unit Tests in Jasmine
\item An in-depth use of external libraries such as d3 or jQuery
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Hubdoc}
\descript{| Software Marketer / Web Developer}

\location{May 2015 – August 2015 | Toronto, ON}
\begin{tightitemize}
\item Developed the entirety of Hubdoc's new Responsive Website (HTML/CSS/JS/jQuery) [www.hubdoc.com]
\item Built Web Scrapers to crawl Accountant/Bookkeeping Directories (Python/JS)
\item Solely handled Hubdoc's Social Media Marketing
\item Managed some of Hubdoc's content marketing, and wrote well received Blog Posts
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Excelgrade e-Learning}
\descript{| CEO \& Founder}

\location{Fall 2006 – Spring 2013 | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item After a visit to India, founded Excelgrade e-Learning to provide the multitude of unemployed teachers with jobs and to aid students in K-12 around the world.
\item Designed and Developed a website using HTML (and later updated using CSS).
\item Managed clients and tutors, and made sure the company was fully functioning.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{University of Tennessee}
\descript{| Cancer Research Intern}

\location{Winter 2012 – Fall 2013 | Knoxville, TN}
Worked with \textbf{\href{http://gsm.utmck.edu/pathology/faculty/orucevic.cfm}{Amila Orucevic}} to perform statistical analyses on thousands of Breast Cancer Patients. We proved that the introduction of adjuvant anti-HER2 treatment has no impact on overall survival, despite common belief. Our research was conducted by acquiring thousands of patient records, and running scripts in Python to extract relevant information to analyze. Results warrant further studies.

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Ongoing Projects
%------------------------------------------------

\section{Ongoing/Future Projects}

\runsubsection{Lemonade Stand}
\descript{| CEO \& Founder}

\location{Spring 2017 – N/A | Waterloo, ON}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightitemize}
	\item Create an application for Android \& iOS devices
    \item Uber style service for a variety of services (primarily food)
    \item Learning ways to integrate safe and automated payment into apps
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Oracle Java Certification}
\descript{| Java SE 7 Programmer I}

\location{Winter 2017 | Waterloo, ON}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightitemize}
	\item I aim to take the Java SE 7 Programmer I Certification Test
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards} 

\begin{tabular}{rll}

2014	 & Avg of 95\%+ & President’s Scholarship of Distinction (UWaterloo)\\
2014	 & GPA of 4.0+ & Member of The American National Honors Society (NHS) \\
2014	 & Top 5 (In-School) & American Math Contest\\
2014	 & School Champion & Euclid Math Contest\\
2014	 & 1\textsuperscript{st} Place (State) & HOSA Medical Math Contest\\
2013 	 & Top 3 (State) & Technology Student Assn. Digital Video Competition \\
2010	 & 1\textsuperscript{st} Place & Bad Dog Theatre Improv Competition \\
2006	 & 1\textsuperscript{st} Place (Toronto) & Kiwanis Youth Monologue Competition \\
2006	 & Person of the Year & TIME Magazine \\
\end{tabular}

\sectionspace % Some whitespace after the section

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
